\chapter{Conclusion}\label{con}

In this chapter, we would like to review the concepts discussed in the earlier sections.
\\
In this thesis, we generate algorithm of bar 2-visibility representations of 2-planar graph such on grid graph. We represent the configuration of 2-planar graphs into specific division. Given an undirected graph $G$, this thesis gives a drawing algorithm that gives bar 2-visibility representations on grid. We give an algorithm for st-numbering of non-planar graph.
\\
In chapter \ref{intro}  we presented a brief overview of the basic graph theoretic and drawing concepts. We discussed about visibility representation of planar graph and further defined briefly bar visibility graph. Then we came into the point of bar k-visibility graph and then we discussed about bar 1-visibility graph,   bar 1-visibility representation, 1-visibility representation, bar 2-visibility graph and bar 2-visibility representation. We have mentioned some previous works which is related to our thesis.
\\
In chapter \ref{preliminaries}, we have given some preliminary ideas on graph theory and algorithmic theory on st-numberingn. The chapter includes some basic concepts of graph that may be outside of the visibility representation but helped in our research in this area.
\\
Chapter \ref{visibility} presents description of visibility representations of planar graph, bar 1-visibility representations of 1-planar graph, 1-visibility representations of 1-planar graph, 2-planar graphs. This chapter gives some the details of the previous results, including the related proofs and descriptions and some part of our thesis work on 2-planar graphs.
\\
Finally, in chapter \ref{visibility}, we present description of bar 2-visibility representations of 2-planar graph. We have described our results on Bar 2-Visibility Representations.
\endinput
