% You do not need to change anything in this file. If you want to
% change the reference style, comment/uncomment the \bibliographystyle
% lines

\clearpage
\renewcommand\bibname{References}
\addcontentsline{toc}{chapter}{References}

% Comment/uncomment as suits you
\bibliographystyle{ieeetr} %% IEEE transaction style
% \bibliographystyle{acm} %% ACM style
% \bibliographystyle{alpha}
\bibliography{cseugthesis}



\begin{thebibliography}{9}

\bibitem{Biggs}
Biggs, N.; Lloyd, E.; Wilson, R. (1986), Graph Theory, 1736-1936, Oxford University Press.

\bibitem{Tutte}
Tutte, W.T. (2001), Graph Theory, Cambridge University Press, p. 30, ISBN 978-0-521-79489-3, retrieved 2016-03-14


\bibitem{R}
R. Tamassia and I. G Tollis. A unified approach to visibility representations of planar graphs. In Discrete and Computational geometry,volume 1, pages 321–341, 1986.



\bibitem{Igor}
FABRICI2007854,The structure of 1-planar graphs,Discrete Mathematics,2007,https://doi.org/10.1016/j.disc.2005.11.056, http://www.sciencedirect.com/science/article/pii/S0012365X06005966,Igor Fabrici and Tomáš Madaras,1-Planar graph, Light graph, Crossing.


\bibitem{Michael}
On Optimal 2- and 3-Planar Graphs of Michael A. Bekos1, Michael Kaufmann1, Chrysanthi N. Raftopoulou2




\bibitem{M}
M. Dean, W. Evans, E. Gethner, J. D. Laison, and M. Safari. Bar k-visibility graphs. Journal of Graph Algorithms and Applications, 11(1):45–59, 2007



\bibitem{S}
S. Fleshner and M. Massow. Thickness of Bar 1-Visibility graphs, volume 4372 of Lecture Notes in Computer Science. Springer-Verlag, 2007.



\bibitem{FJ}
Franz J. Brandenburg,1-Visibility Representations of 1-Planar Graphs,Journal of Graph Algorithms and Applications http://jgaa.info/ vol. 18, no. 3, pp. 421{438 (2014) DOI: 10.7155/jgaa.00330}




\bibitem{JOUR}
JOUR , Zaiping, Song, Ning ,2017/05/31 , On the minimum weight of a 3-connected 1-planar graph ,10.4134/BKMS.b160296 , Bulletin of the Korean Mathematical Society.



\bibitem{G}
G. Di Battista, P. Eades, R. Tamassia, and I. G. Tollis. Graph Drawing:Algorithms for the Visualization of Graphs. Prentice-Hall, Upper Saddle River, New Jersey, 1999.



\bibitem{Otten}
J. Otten and J. G. Van Wijk. Graph representation in interactive layout design. In the Proceedings of IEEE Intternational Symposium On Circuits and Systems, pages 914–918, 1978.





\bibitem{alam}
Alam M.J., Brandenburg F.J., Kobourov S.G. (2013) Straight-Line Grid Drawings of 3-Connected 1-Planar Graphs.https://doi.org$/10.1007/978-3-319-03841-4_8.$




\bibitem{Nishizeki}
T. Nishizeki and M. S. Rahman. Planar Graph Drawing. World Scientific, Singapore, 2004.




\bibitem{Christopher}
On Sparse Maximal 2-Planar Graphs ,Christopher Auer, Franz J. Brandenburg,Andreas Gleißner, and Kathrin Hanauer University of Passau, 94030 Passau, Germany{auerc,brandenb,gleissner,hanauer}@fim.uni-passau.de.



\bibitem{tutte}
{Tutte, W.T.: How to draw a graph. Proc. London Math. Society 13(52), 743–768 (1963)}




\bibitem{madaras}
T. Madaras I. Fabrici. The structure of 1-planar graphs. Journal on Discrete Mathematics, 307:854–865, 2007.



\bibitem{sultana}
Sultana, Shaheena and Rahman, Md. Saidur and Roy, Arpita and Tairin, Suraiya . Bar 1-Visibility Drawings of 1-Planar Graphs,2014.


\bibitem{michael}
On Optimal 2- and 3-Planar Graphs. Michael A. Bekos, Michael Kaufmann, Chrysanthi N. Raftopoulou, 2017.


\bibitem{p}
P. Eades and G. Liotta. Right angle crossing graphs and 1-planarity. Appeared to GD 2011 proceedings of the symposium on Graph Drawing,2011.



\bibitem{Even}
S. Even A. Lempel and I. Cederbaum. An algorithm for planarity testing of graphs. P. Rosestiehl(ed.) Theory of Graphs: International Symposium July 1966, pages 215–232, 1967.


\bibitem{stein}
K. S. Stein. Convex maps. In Proc. of American Mathematical Society, volume 1353 of Lecture Notes in Computer Science, pages 248–261. Springer-Verlag, 1997.



\bibitem{fary}
I. Fary. On straight line representations of planar graphs. Acta Sci. Math. Szeged., 11:229–233, 1948.



\bibitem{Alempel}
A. Lempel, S. Even and I. Cederbaum, An algorithm for planarity testing of graphs, in: P. 
Rosenstiehl (ed.j, Theory of Graphs: Irttemational Symposium,Jufy1956(Gordon and Breach, New York, 1967)  21~232.CJ. S. Lueker and  K.

\bibitem{PachNToth}
Pach, J. & Tóth, G. Combinatorica (1997) 17: 427. https://doi.org/10.1007/BF01215922 Springer-Verlag; Print ISSN 0209-9683; Online ISSN 1439-6912


\end{thebibliography}
\endinput
